Tree establishment in models of forest dynamics: a key priority for further research

### 2023-02-16 manuscript/manuscriptRW.Rmd
firs attempt to re-define paper questions

>>>>

NEW

1) Are models of forest dynamics capturing accurately tree ingrowth
levels, initial tree diversity and mortality in tree establishment?

2) Species specific recruitment values in ennvironmental gradients?

3) Are the models traits linked to the tree establishment values?

environmental gradients?

2) Are they matching the initial species composition of the tree
ingrowth layer? And

3), do they correctly represent the mortality in tree establishment?
